\section{Work}

%TODO find a better title
\subsection{Tools}
\subsubsection{Generating $k$-connected random graphs}
\paragraph{}
In order to test our implementation of the algorithm proposed in~\cite{JS94},
$k$-connected  graphs had to be generated. We have implemented two methods,
although the graphs produced are not uniformly randomised.

\paragraph{}
The first method is based on the vertex degree. To be $k$-connected, a graph
needs to have vertices of degree at least $k$. For each vertex, edges are added
until the vertex has degree at least $k$. Once this procedure achieved, then
possibly the reduced graph is $k$-connected.

\paragraph{}
%TODO explain why : complete component so that the graph is localy dense
Since this first method is not deterministic, we have implemented another method
which produces a $k$ connected graph by creating several complete
components and linking them together. The algorithm is described in
Algorithm~\ref{graphGenerator}.

\begin{algorithm}[!h]
  \KwData{$k$ the connectivity,\\ $N$ the number of components,\\ $n$ the size of components}
  \KwResult{A $k$-connected graph}
  $components = \emptyset$\;
  $edges = \emptyset$\;
  \For{i = 1 to N}{
    $components = components \cup newCompleteComponent(n)$
  }
  \For{i = 1 to N-1}{
    \For{j = 1 to k}{
      $edges = edges \cup (components[i][j], components[i+1][j])$
    }
  }
  $g = newGraph(components, edges)$\;
  \Return{$g$}\;
  \caption{\label{graphGenerator}$k$-connected graph generator}
\end{algorithm}

\paragraph{}
First, the complete components are generated. Then $k$ edges are added between the 
first and the second components, $k$ edges are added between the second and the 
third ones and so on.

%TODO explain clearly
\paragraph{}
The edges between every pair of components are not randomly selected, otherwise
it would be easy to diconnect the graph by removing less than $k$ vertices. So
we procede in the following way for adding the edges. Suppose that the
vertices of each component are numbered from 1 to the order of the component.
The edges between the vertex 1 of the first component and the vertex 1 of the
second component are selected. The same process is repeated for the second
vertices to the $k$-th vertices and then  for the other components. At the end,
the resulting graph is $k$-connected.


 
\subsubsection{Calculating a sparse spanning subgraph}
% Necessity of implementing FOREST
\paragraph{}
In order to reduce the execution time of the main algorithm, we had to
implement another algorithm described in~\cite{NaIb92}.

% Algo description
\paragraph{}
This algorithm is called \verb!FOREST! and takes a graph $G=(V,E)$ as a parameter.
The output is slightly more complicated since it does not simply return the
sparse spanning subgraph. Instead, the algorithm returns an array $A$ of set of
edges. The size of the array returned is $|E(G)|$. The graph induced by the
set of edges $\bigcup \limits_{i=1}^k E_i$
is $k$-connected, if the connectivity of $G$ is greater or equal to $k$.

% Specific data structure
\paragraph{}
The main difficulty about the implementation of this algorithm was the use of a
specific data structure that allows an access to the maximum, an insertion and
a deletion of an element with a constant amortized cost. Even if such a
structure does not exist for any kind of utilisation, it is possible to create
one which has all the required properties for this algorithm, since the
utilisation is very specific and since an element has always an integer
associated value that can grow only from 1 at each step.

% More details ?

%Tests
\paragraph{}
Tests have been created and run in order to prove that the result of our
implementation of the \verb!FOREST! algorithm was corresponding to the main
objective:
$$\forall k, k \leq K(G),K(V,\bigcup \limits_{i=1}^k E_i) = k.$$

\paragraph{}
This test has been validated on simple graphs, but it has also been seen that
our implementation did not produce the expected result if the input is a
multigraph. We checked this property by following the algorithm on small
multigraphs and this showed us that the problem was not coming from the
implementation, but rather from the algorithm. Since we are working on simple
graphs, this was not really a problem for our tests.

\subsection{Implementing the algorithm}
% Separation in function + misplaced lines
\paragraph{}
In order to facilitate the comprehension of the algorithm implementation and
the debugging, we choose to present the different parts of the algorithm. While
we were implementing it, we also noted that some lines where misplaced, breaking
the coherency of the algorithm.

% Choosing the appropriated data structures
\paragraph{}
In order to have the same complexity as the one proved in the paper, we sticked
to the same data structures. In order to accept graphs where vertices are not
only integers, we added an HashMap, allowing an access in constant time to the
index of a vertex.

% Tree Manipulation
\paragraph{}
In the library we were using, spanning graphs were not designed to be modified.
We created our own basic class which was handling trees with the needed methods
like cutting a tree on a specific vertex.

\subsection{Criticism}
\subsubsection{Finding a counter-example}
% Not failing on some entries but on some executions
\paragraph{}
Once the main issues of the implementation of the algorithm were solved, we
had still some issues with the algorithm falling in endless loops. Our
investigations on this specific problem ended with the fact that the problem was
coming from the algorithm and not from the implementation. This was ensured by
verifying the validity of the execution of our algorithm step by step on these
specific problematic instances.

\input{report/CounterExample}

\subsubsection{Counter-example in general case}
\paragraph{}
In order to ensure that $k=2$ is not a specific case for which the algorithm
presented in~\cite{JS94} can loop endlessly, we present a proof that an
execution can loop endlessly for any $k$.

\paragraph{}
The proof is by induction. Since we have already exhibited
a counter-example for $k=2$, we only need to prove the induction step.

\paragraph{}
Let $G$ be a $k$-connected graph for which the algorithm has a
probability of looping endlessly strictly greater than $0$ for the entry
$\{r_1,r_2, \dots, r_k\}$ and $\{n_1,n_2, \dots, n_k\}$. Then a graph $G'$ can
be found such that $G'$ is $k+1$-connected and there exists an entry for which
the algorithm has a probability of looping endlessly strictly greater than $0$.

\paragraph{Proof:}
If we create $G'$ by adding a new vertex $v$ connected to every vertex of $G$,
i.e. $V(G') = V(G) \cup v$ and
$E(G') = E(G) \cup \bigcup \limits_{u \in V(G)} \{u,v\}$, it is obvious that
$G'$ is $k+1$-connected, since every minimal vertex cut of $G$ needs to have
one additional vertex in order to be a cut of $G'$.

\paragraph{}
An execution of the algorithm with $G'$, $\{r_1,r_2, \dots, r_k, v\}$,
$\{n_1,n_2, \dots, n_k, 1\}$ as input has a probability of looping
endlessly strictly greater than $0$, as the introduced vertex $v$ has no
influence
since the associated tree is full since the beginning and the new edges
are not useable.
% Bad presentation ...
\subsection{Improvements}
\subsubsection{Vertex selection condition}
\paragraph{}
To select the vertex to swap between two trees, the article algorithm bases its 
choices on the vertex degree. As we have seen before, the selection of specific
vertices can lead to an endless loop. Choosing the vertex with the lowest degree
can cut a long branch of the tree, whereas select another vertex with a greater
degree removes less vertices to the tree.

That is why, we have modified the vertex selection condition. Rather than basing
the selection condition on the vertex degree, we base it on the number of 
descendants. So, when a vertex is swapped the minimum number of vertices is
removed from the tree.

\paragraph{}
This modification allows to avoid the endless loop for the counter-example
presented above. However there are still some executions on other graphs which
are falling into endless loops.

\subsubsection{Detecting endless loops}
\paragraph{}
A counter-example which shows that the algorithm can fall in endless loops have
been exhibited. This raises one question: is it possible to detect when there
is an endless loop? An improvement has been added to the algorithm in order to
detect such situations. To do so, we save the last root index where we have
added or swapped a vertex. If the saved index is equal to the current root index
and no vertex have been added or swap then it means that the algorithm has
entered in an endless loop. Then the execution is stopped.
